Birth Spacing in the Presence of Son Preference and Sex-Selective \\ Abortions: India's Experience over Four Decades

### 2018-04-19 presentations/2018-paa-poster.tex
Minor edits

The model is a discrete time, non-proportional, competing risk 
hazard model with two exit states: either a boy or a girl is born.
\begin{description}
\item[Competing risk] captures that
parents can choose the sex of children born with access to prenatal 
sex determination.
\item[Non-proportional hazard] captures that sex composition and 
the use of sex selection likely affect the shape of the hazard 
functions across groups.
\end{description}

@@

Two important, interconnected, questions:
What is the connection between falling fertility and the 
use of sex selection and is the use of sex selection increasing 
or decreasing over time?

@@

Broader questions:
\begin{itemize}
\item To what extent are improvements in health for girls
relative to boys the result of selection, the longer spacing between
births, or changing son preference?
\item What is the interaction between female labor force participation
and the use of sex selection?
\end{itemize}

>>>>

The model is a discrete time, non-proportional, competing risk 
hazard model with two exit states: either a boy or a girl is born.
\begin{description}
\item[Competing risk] captures that
parents can choose the sex of children born with access to prenatal 
sex determination.
\item[Non-proportional hazard] captures that sex composition and 
the use of sex selection likely affect the shape of the hazard 
functions across groups and that use of sex selection may vary
within a spell.
\end{description}

@@

The results lead to two important, interconnected, questions:
What is the connection between falling fertility and the 
use of sex selection, and is the use of sex selection increasing 
or decreasing over time?

@@

There are also two broader questions:
\begin{itemize}
\item To what extent are improvements in health for girls
relative to boys the result of selection, the longer spacing between
births, or changing son preference or higher value placed on girls
with fewer of them around?
\item What is the interaction between female labor force participation
and the use of sex selection?
\end{itemize}
